An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors

### 2021-03-21 comment.tex
a bit of Methods

\begin{document}
\title{An Accurate Model for SARS-CoV-2 pooled RT-PCR Tests Errors}

@@

\section{Methods}
Before delving into our probabilistic assumptions, we briefly explain
the process of testing for SARS-CoV-2 by RT-PCR in
Section~\ref{subsec:rtpcr}. Our exposition intentionally avoids many
details and a comprehensive review of RT-PCR can be found in
\cite{COVID-RTPCR, PCRBook}. We then present the \emph{common
  assumption} in Section~\ref{subsec:common} and refute it in
Section~\ref{subsec:refute}. Our model is presented in
Section~\ref{subsec:ours}.

@@

\subsection{The common assumption}\label{subsec:common}
Previous studies of group testing strategies assumed that the
false-negative probability does not depend on the number of infected
samples, but merely on the existence of at least one such sample in a
pool \cite{Kim, OptimalDorfmanPool}. Current studies of pooling in the
context of SARS-CoV-2 also employ similar assumptions
\cite{Simplistic1, Simplistic2}. Specifically, these studies assume
that the probability of a negative result is the same for a pool with
a single sample coming from an infected individual and (e.g.)
five. Explicitly:

>>>>

\begin{document}
\title{An Accurate Model for SARS-CoV-2 pooled RT-PCR Test Errors}

@@

\section{Methods}
Before delving into our probabilistic assumptions, we briefly explain
the process of testing for SARS-CoV-2 by RT-PCR in
Section~\ref{subsec:rtpcr}. Our exposition intentionally avoids many
details, and a comprehensive review of RT-PCR can be found in
\cite{COVID-RTPCR, PCRBook}. We then present the \emph{common
  assumption} in Section~\ref{subsec:common} and refute it in
Section~\ref{subsec:refute}. Our model is presented in
Section~\ref{subsec:ours}.

@@

\subsection{The common assumption}\label{subsec:common}
Previous studies of group testing strategies assumed that the
false-negative probability does not depend on the number of infected
samples, but merely on the existence of at least one such sample in a
pool \cite{Kim, OptimalDorfmanPool}. Current studies of pooling in the
context of SARS-CoV-2 also employ similar assumptions
\cite{Simplistic1, Simplistic2}. Specifically, these studies assume
that the probability of a negative result is the same for a pool with
a single sample coming from an infected individual and several
 samples from infected individuals. Explicitly:
